\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{STEM Fellowship Big Data Challenge 2020} \\ [10pt] \huge Deep learning transcriptomic model for prediction of pan-drug chemotherapeutic sensitivity \\

### 2020-06-26 manuscript/manuscript.tex
added fig ref

The neural network with 1 hidden layer performed poorly with 71.6\% accuracy. However, the 1 hidden layer model had the highest precision 95.5\% of the models (92.6\% for 5 hidden layers, 87.7\% for 10 hidden layers, 87.7\% for 15 hidden layers). The poor accuracy for the 1 hidden layer model was accounted for with a low negative predictive value (55.4\%; 80.5\% for 5 hidden layers, 100\% for 10 hidden layers, 100\% for 15 hidden layers). It was determined that the most accurate model was the neural network with 10 hidden layers (90.8\% accuracy; 71.6\% for 1 hidden layer, 88.1\% for 5 hidden layers, 85.3\% for 15 hidden layers).

>>>>

The neural network with 1 hidden layer performed poorly with 71.6\% accuracy. However, the 1 hidden layer model had the highest precision 95.5\% of the models (92.6\% for 5 hidden layers, 87.7\% for 10 hidden layers, 87.7\% for 15 hidden layers). The poor accuracy for the 1 hidden layer model was accounted for with a low negative predictive value (55.4\%; 80.5\% for 5 hidden layers, 100\% for 10 hidden layers, 100\% for 15 hidden layers). It was determined that the most accurate model was the neural network with 10 hidden layers (90.8\% accuracy; 71.6\% for 1 hidden layer, 88.1\% for 5 hidden layers, 85.3\% for 15 hidden layers; Fig. \ref{fig:nnet}).
